Parallelization of Push-based System for Molecular Simulation Data Analysis

### 2016-01-21 paper/paperSource.tex
paper changed

\documentclass[10pt,journal,final,letterpaper,twocolumn]{IEEEtran}
%\documentclass{ssdbm}
\usepackage{wrapfig,subfigure,setspace,verbatim,cite,url,graphicx,float}
\usepackage{algorithmic,amsfonts,amssymb,amsmath,calc,calrsfs,cleveref}
\usepackage{epstopdf}
%\usepackage{fixltx2e}

@@

%\thanks{* These authors contributed equally to this work.}
\thanks{$\dagger$ Author to whom all correspondence should be sent.}
\thanks{Vladimir Grupcev and Yi-Cheng Tu are with the Department of Computer
Science and Engineering, University of South Florida, 4202 E. Fowler
Ave., ENB 118, Tampa, FL 33620, U.S.A. Emails:
vgrupcev@mail.usf.edu, ytu@cse.usf.edu}
\thanks{Joseph Fogarty and Sagar Pandit are with the Department of Physics,
University of South Florida, 4202 E. Fowler Ave., ISA 2019, Tampa,
FL 33620, U.S.A. Emails: jcfogart@mail.usf.edu, pandit@usf.edu} }

@@

\section{Introduction}\label{sc:intro}
The amount of data generated by scientific applications running on
advanced computer simulation systems as well as the new improved
experimental devices is growing rapidly. This big volume of data is
imposing a significant stress on the data analysis software. Even
though the existing data analysis systems are configured to deal
with large volume of data, they are not optimized for high
throughput data analysis. Often times, the data is available only
for certain period of time (e.g., streams) so the analyzing system
should react to it in a very efficient way. On top of the big amount
of data, another challenge that is being imposed to the data
analysis systems is that the data is usually being accessed through
high-level analytical queries which computation is a lot more
complex than the computation of simple aggregates. Some of these
queries are usually the bottleneck of the data analysis systems,
because they take a lot of time (often many days) to be executed and
the systems are not designed to handle multiple queries on the same
data stream at the same time, thus decreasing the overall efficiency
of the data analysis.

@@

\bibliographystyle{IEEEtran}
\bibliography{push-based-MS}
\begin{comment}
\begin{IEEEbiographynophoto}{Vladimir Grupcev}
received a BS degree in Applied Mathematics \& Computer Science from
University of Ss. Cyril and Methodius, Macedonia in 2005; Master's
degree in Mathematics from University of South Florida in 2007. He
is currently a PhD student in the department of Computer Science \&
Engineering at the University of South Florida. His area of interest
includes scientific data management and high performance computing.
\end{IEEEbiographynophoto}
\vspace{-10mm}
\begin{IEEEbiographynophoto}{Yi-Cheng Tu}
received a Bachelor's degree in horticulture from Beijing
Agricultural University, China, and MS and PhD degrees in computer
science from Purdue University (2003; 2007). He is currently an
assistant professor in the department of Computer Science \&
Engineering at the University of South Florida. His research is in
energy-efficient database systems, scientific data management, high
performance computing and data stream management systems.
\end{IEEEbiographynophoto}
\vspace{-10mm}
\begin{IEEEbiographynophoto}{Sagar Pandit}
Dr. Sagar Pandit is an Assistant Professor of Physics at the
University of South Florida. He received his Ph.D. from the
Department of Physics, University of Pune, in 1999 in the area of
Dynamical systems. Later, his research shifted to Biological
Physics, specifically membrane physics. His current research
interests include  biomembranes, mathematical modeling of complex
biological and social systems, dynamical systems, and computational
approaches toward addressing problems in these fields.
\end{IEEEbiographynophoto}
\end{comment}

% if you will not have a photo
%\begin{biographynophoto}{John Doe}
%Biography text here.
%\end{biographynophoto}

% insert where needed to balance the two columns on the last page

>>>>

\documentclass[10pt,journal,final,letterpaper,twocolumn,conference]{IEEEtran}
%\documentclass{ssdbm}
\usepackage{wrapfig,subfigure,setspace,verbatim,cite,url,graphicx,float}
\usepackage{algorithmic,amsfonts,amssymb,amsmath,calc,calrsfs,cleveref}
\usepackage{epstopdf,filecontents,lipsum}
%\usepackage{fixltx2e}

@@

%\thanks{* These authors contributed equally to this work.}
\thanks{$\dagger$ Author to whom all correspondence should be sent.}
\thanks{Iliiazbek Akhmedov and Yi-Cheng Tu are with the Department of Computer Science and Engineering, University of South Florida, 4202 E. Fowler Ave., ENB 118, Tampa, FL 33620, U.S.A. Emails:
akhmedovi@mail.usf.edu, ytu@cse.usf.edu}
\thanks{Joseph Fogarty and Sagar Pandit are with the Department of Physics,
University of South Florida, 4202 E. Fowler Ave., ISA 2019, Tampa,
FL 33620, U.S.A. Emails: jcfogart@mail.usf.edu, pandit@usf.edu} }

@@

\section{Introduction}\label{sc:intro}

In various sciences simulation systems take big place and often times they may be very important for results. One of such sciences, which is primarily related to this paper, is physics. In this case, from computer engineering point of view, simulations generally have the following flow:

\vspace{5mm}

{\small
\begin{enumerate}
	\item initial physical properties are given to simulation software as arguments which are interpreted and provided in a language defined by the software
	\item then it runs for given amount of time that can generally last from milliseconds to months
	\item finally, the file generated during the simulation is analyzed to extract useful information
\end{enumerate}
}

\vspace{3mm}

The amount of data generated by scientific applications running on
advanced computer simulation systems as well as the new improved
experimental devices is growing rapidly. This big volume of data is
imposing a significant stress on the data analysis software. Even
though the existing data analysis systems are configured to deal
with large volume of data, they are not optimized for high
throughput data analysis. Often times, the data is available only
for certain period of time (e.g., streams) so the analyzing system
should react to it in a very efficient way. On top of the big amount
of data, another challenge that is being imposed to the data
analysis systems is that the data is usually being accessed through
high-level analytical queries which computation is a lot more
complex than the computation of simple aggregates. Some of these
queries are usually the bottleneck of the data analysis systems,
because they take a lot of time (often many days) to be executed and
the systems are not designed to handle multiple queries on the same
data stream at the same time, thus decreasing the overall efficiency
of the data analysis.

@@

\bibliographystyle{IEEEtran}
\bibliography{references.bib}
